---
title: "BIOSTAT620_table1"
author: "Ruoer Bei"
date: "2024-04-19"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(dplyr)
library(tableone)
library(knitr)
library(tableone)
library(readxl)
```

```{r}
#hafshlsgjg
#hdlfsjg;
#ldsjfl
```

```{r}


data <- read_excel("/Users/ruoerbei/Documents/BIOSTAT620/BIOSTAT620_project2/completed_data3.xlsx")

data$Treatment <- as.factor(data$Treatment)

vars <- c("Total.ST.min", "Social.ST.min", "Pickups", "apps", "devices", "procrastination_score", "workmate", "X2_academic_talk", "non_academic", "pets", "age", "cousre_credit", "siblings" )

strata <- "Treatment"

table1 <- CreateTableOne(vars = vars, strata = strata, data = data, factorVars = c("Treatment"))

print(table1)



```

+----------------------------------+-----------------+-----------------+--------------+
|                                  | A               | B               | p_value      |
+==================================+=================+=================+==============+
| n                                | ```             | ```             |              |
|                                  | 928             | 1225            |              |
|                                  | ```             | ```             |              |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Total.ST.min (mean (SD))         | 407.17 (210.25) | 394.14 (182.51) | 0.125        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Social.ST.min (mean (SD))        | 191.78 (152.53) | 205.22 (123.07) | 0.024        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Pickups (mean (SD))              | 97.19 (52.17)   | 99.53 (40.65)   | 0.243        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Apps (mean (SD))                 | 3.95 (2.05)     | 4.14 (1.64)     | 0.015        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Devices (mean (SD))              | 2.76 (1.10)     | 2.92 (1.04)     | 0.001        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Procrastinationscore (mean (SD)) | 36.43 (8.19)    | 38.24 (11.61)   | <0.001       |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Age (mean (SD))                  | 23.59 (2.30)    | 22.98 (0.99)    | <0.001       |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Workmate (mean (SD))             | 0.93 (1.04)     | 0.95 (0.91)     | 0.686        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| X2_academic_talk (mean (SD))     | 0.93 (0.95)     | 1.01 (0.87)     | 0.034        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Non_academic (mean (SD))         | 1.27 (1.42)     | 1.59 (2.09)     | <0.001       |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Pets (mean (SD))                 | 0.08 (0.28)     | 0.05 (0.22)     | 0.002        |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Cousre_credit (mean (SD))        | 12.92 (4.12)    | 13.59 (2.36)    | <0.001       |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+
| ```                              | ```             | ```             | ```          |
| Siblings (mean (SD))             | 0.82 (1.92)     |  0.45 (0.88)    | <0.001       |
| ```                              | ```             | ```             | ```          |
+----------------------------------+-----------------+-----------------+--------------+

Table 1: Summary Table for Screentime and Baseline

+------------------------------------------+-----------------+------------------+--------------+
|                                          | A               | B                | P value      |
+==========================================+=================+==================+==============+
| n                                        | 11              | 17               |              |
+------------------------------------------+-----------------+------------------+--------------+
| Total Screen Time (in Mins) (mean (SD))  |                 |                  |              |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-01-16 to 2024-03-27                 | 414.93 (204.67) | 397.041 (179.59) | ```          |
|                                          |                 |                  | 0.044        |
|                                          |                 |                  | ```          |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-03-28 to 2024-04-02                 | 309.51 (241.44) | 359.88 (204.84)  | 0.156        |
+------------------------------------------+-----------------+------------------+--------------+
| Social Screen Time (in Mins) (mean (SD)) |                 |                  |              |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-01-16 to 2024-03-27                 | 196.13 (154.42) | 205.81 (122.95)  | 0.134        |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-03-28 to 2024-04-02                 | 135.89 (115.34) | 198.67 (120.80)  | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+
| Pickups (mean (SD))                      |                 |                  |              |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-01-16 to 2024-03-27                 | 98.22 (51.45)   | 102.68 (40.28)   | 0.037        |
+------------------------------------------+-----------------+------------------+--------------+
| 2024-03-28 to 2024-04-02                 | 86.61 (60.14)   | 66.61 (28.88)    | 0.011        |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Apps (mean (SD))               | 3.95 (2.05)     | 4.14 (1.64)      | 0.02         |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Devices (mean (SD))            | 2.76 (1.10)     | 2.92 (1.04)      | 1.00\*e\^-3  |
+------------------------------------------+-----------------+------------------+--------------+
| Procrastination Score (mean (SD))        | 36.43 (8.19)    | 38.24 (11.61)    | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+
| Age (mean (SD))                          | 23.59 (2.30)    | 22.98 (0.99)     | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Workmate Before(mean (SD)      | 0.93 (1.04)     | 0.95 (0.91)      | 0.69         |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Academic Talks (mean (SD))     | 0.93 (0.95)     | 1.01 (0.87)      | 0.03         |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Non-academic Talks (mean (SD)) | 1.27 (1.42)     | 1.59 (2.09)      | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+
| Number of Pets (mean (SD))               | 0.08 (0.28)     | 0.05 (0.22)      | 2.00\*e\^-3  |
+------------------------------------------+-----------------+------------------+--------------+
| Course credits (mean (SD))               | 12.92 (4.12)    | 13.59 (2.36)     | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+
| Siblings (mean (SD))                     | 0.82 (1.92)     | 0.45 (0.88)      | \<0.001      |
+------------------------------------------+-----------------+------------------+--------------+

```{r}
library(tableone)
library(readxl)
library(dplyr)


data$Date <- as.Date(data$Date)  # Ensure 'Date' is in Date format
period1 <- subset(data, Date >= as.Date("2024-01-16") & Date <= as.Date("2024-03-27"))
period2 <- subset(data, Date >= as.Date("2024-03-28") & Date <= as.Date("2024-04-02"))

calc_stats <- function(df, vars) {
  lapply(vars, function(var) {
    c(Mean = mean(df[[var]], na.rm = TRUE),
      Variance = var(df[[var]], na.rm = TRUE),
      SD = sd(df[[var]], na.rm = TRUE))
  })
}


time_vars <- c("Total.ST.min", "Social.ST.min", "Pickups")
stats_period1 <- calc_stats(period1, time_vars)
stats_period2 <- calc_stats(period2, time_vars)


other_vars <- c("apps", "devices", "procrastination_score", "workmate", "X2_academic_talk", "non_academic", "pets", "age", "cousre_credit", "siblings")
table1 <- CreateTableOne(vars = other_vars, strata = "Treatment", data = data, factorVars = c("Treatment"))


print(table1)


print("Statistics from Jan 16th to March 27th:")
print(stats_period1)

print("Statistics from March 28th to April 2nd:")
print(stats_period2)

```

```{r}

library(readxl)
library(dplyr)

data <- read_excel("/Users/ruoerbei/Documents/BIOSTAT620/BIOSTAT620_project2/completed_data3.xlsx")

data$Date <- as.Date(data$Date)

date_range1_start <- as.Date("2024-01-16")
date_range1_end <- as.Date("2024-03-27")
date_range2_start <- as.Date("2024-03-28")
date_range2_end <- as.Date("2024-04-02")

data_range1 <- data %>%
  filter(Date >= date_range1_start & Date <= date_range1_end)

data_range2 <- data %>%
  filter(Date >= date_range2_start & Date <= date_range2_end)

mean_var_range1 <- data_range1 %>%
  summarise(
    Mean_Total_ST_min = mean(Total.ST.min, na.rm = TRUE),
    Variance_Total_ST_min = var(Total.ST.min, na.rm = TRUE),
    Mean_Social_ST_min = mean(Social.ST.min, na.rm = TRUE),
    Variance_Social_ST_min = var(Social.ST.min, na.rm = TRUE),
    Mean_Pickups = mean(Pickups, na.rm = TRUE),
    Variance_Pickups = var(Pickups, na.rm = TRUE)
  )

mean_var_range2 <- data_range2 %>%
  summarise(
    Mean_Total_ST_min = mean(Total.ST.min, na.rm = TRUE),
    Variance_Total_ST_min = var(Total.ST.min, na.rm = TRUE),
    Mean_Social_ST_min = mean(Social.ST.min, na.rm = TRUE),
    Variance_Social_ST_min = var(Social.ST.min, na.rm = TRUE),
    Mean_Pickups = mean(Pickups, na.rm = TRUE),
    Variance_Pickups = var(Pickups, na.rm = TRUE)
  )
print(mean_var_range1)
print(mean_var_range2)

```

```{r}
library(readxl)
library(dplyr)

data <- read_excel("/Users/ruoerbei/Documents/BIOSTAT620/BIOSTAT620_project2/completed_data3.xlsx")

data$Date <- as.Date(data$Date)


date_range1_start <- as.Date("2024-01-16")
date_range1_end <- as.Date("2024-03-27")
date_range2_start <- as.Date("2024-03-28")
date_range2_end <- as.Date("2024-04-02")

# Filter data for the two date ranges and intervention types using the 'Treatment' column
data_range1_A <- filter(data, Date >= date_range1_start & Date <= date_range1_end & Treatment == "A")
data_range1_B <- filter(data, Date >= date_range1_start & Date <= date_range1_end & Treatment == "B")
data_range2_A <- filter(data, Date >= date_range2_start & Date <= date_range2_end & Treatment == "A")
data_range2_B <- filter(data, Date >= date_range2_start & Date <= date_range2_end & Treatment == "B")


calculate_stats <- function(data) {
  data %>%
    summarise(
      Mean_Total_ST_min = mean(Total.ST.min, na.rm = TRUE),
      Variance_Total_ST_min = var(Total.ST.min, na.rm = TRUE),
      Mean_Social_ST_min = mean(Social.ST.min, na.rm = TRUE),
      Variance_Social_ST_min = var(Social.ST.min, na.rm = TRUE),
      Mean_Pickups = mean(Pickups, na.rm = TRUE),
      Variance_Pickups = var(Pickups, na.rm = TRUE)
    )
}

stats_range1_A <- calculate_stats(data_range1_A)
stats_range1_B <- calculate_stats(data_range1_B)
stats_range2_A <- calculate_stats(data_range2_A)
stats_range2_B <- calculate_stats(data_range2_B)

print("Stats for Intervention A from 2024-01-16 to 2024-03-27:")
print(stats_range1_A)
print("Stats for Intervention B from 2024-01-16 to 2024-03-27:")
print(stats_range1_B)
print("Stats for Intervention A from 2024-03-28 to 2024-04-02:")
print(stats_range2_A)
print("Stats for Intervention B from 2024-03-28 to 2024-04-02:")
print(stats_range2_B)



```

```{r}

compare_means <- function(data_A, data_B) {
  list(
    Total_ST_min = t.test(data_A$Total.ST.min, data_B$Total.ST.min, na.action = na.exclude),
    Social_ST_min = t.test(data_A$Social.ST.min, data_B$Social.ST.min, na.action = na.exclude),
    Pickups = t.test(data_A$Pickups, data_B$Pickups, na.action = na.exclude)
    # Uncomment below for Mann-Whitney U test if data is not normally distributed
    # Total_ST_min = wilcox.test(data_A$Total.ST.min, data_B$Total.ST.min, na.action = na.exclude),
    # Social_ST_min = wilcox.test(data_A$Social.ST.min, data_B$Social.ST.min, na.action = na.exclude),
    # Pickups = wilcox.test(data_A$Pickups, data_B$Pickups, na.action = na.exclude)
  )
}

p_values_range1 <- compare_means(data_range1_A, data_range1_B)
p_values_range2 <- compare_means(data_range2_A, data_range2_B)

p_values_range1

p_values_range2

```
